\normalsize \textsc{Large-Scale Data Analysis Techniques} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{A Review on Multi-Label Learning Algorithms}} \HRule{2pt} \\ [0.5cm] \normalsize \today \vspace*{5\baselineskip}

### 2018-01-20 Paper/PaperReport/PaperReport.tex
Update project report

\documentclass[12pt]{report}
\usepackage[a4paper]{geometry}
\usepackage[myheadings]{fullpage}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx, wrapfig, subcaption, setspace, booktabs}
\usepackage[T1]{fontenc}
\usepackage[font=small, labelfont=bf]{caption}
\usepackage{fourier}
\usepackage[protrusion=true, expansion=true]{microtype}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{url, lipsum}
\usepackage{listings}
\usepackage{float}
\usepackage{todonotes}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\graphicspath{{images/}}

@@

	\begin{itemize}
		\item \textbf{Example-based: }This kind of metrics evaluate multi-labeled performance on each example and then the result is spread to the whole dataset. The metrics are divided into two perspectives:
      \todos{Form them up into a table}
		\begin{itemize}
			\item Classification:
        \begin{table}
          \centering
          \begin{tabular}{cc} 
          \toprule
            one & two \\
          \midrule
            one & two \\
            one & two \\
          \bottomrule
          \end{tabular}
          \caption{Evaluation metrics for multi-label learning}
          \label{label:evaluation_metrics}
        \end{table}

@@

	\subsection*{Problem Transformation Methods}
	\addcontentsline{toc}{subsection}{Problem Transformation Methods}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.9\textwidth]{pt.png}
		\caption{Problem Transformation Algorithms}
		\centering
	\end{figure}

@@

	\subsubsection*{Claibrated Label Ranking}
	\addcontentsline{toc}{subsubsection}{Claibrated Label Ranking}
	This algorithm transforms the learning problem into a label pairwise comparison ranking problem. For $q$ labels, $q(q-1)/2$ binary classfiers are generated by pairwise comparison and a binary algorithm $h_{jk}(x)$ is used. Firstly, training sets $D_{jk}$ are constructing, where $D_{jk}: \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. The learning system votes for each example and if $h_{jk}(x)>0$, then $x_i$ is associated with label $y_j$, otherwise $y_j$ is irrelevant and $x_i$ is assigned to $y_k$. For unknown instances, classifiers' votes are aggregated and ranked. In addition, a virtual label $y_v$ is used as an artificial splitting point between relevant and irrelevant labels.

	This is a second-order approach algorithm using a one-vs-one scheme. The advantage of this method is that it smooths out the class-imbalance problem (where the number of a class positives is much less than the other's class positives). The disadvantage is the number of classifiers is quadratic to $|Y|$, compared to linear for Binary Relevance algorithm. One improvement to this issue is to use pruning methods to reduce the search space.

	\subsubsection*{Random k-Labelsets}
	\addcontentsline{toc}{subsubsection}{Random k-Labelsets}
	Random k-labelsets algorithm transforms the multi-label learning problem into an ensemble of multi-class classification problems where each component targets a random subset of $Y$, that appears in $X$ classified with Label Powerset (LP) techniques. In more detail, the multi-label dataset is transformed into single-label data by treating each distinct labelset as a new class. Each training example is reassigned with the new mapped class and classified through regular single-label classification. An instance $x_i$ is assigned to label $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible that this label can get. For unseen instances $x$, LP predicts its associated label set $Y$ by querying the prediction of multi-class classifier and then mapping it back to the power set of $Y$.

	This is a high-order approach algorithm, utilizing label correlations. However, there are two limitations in terms of practical feasibility:

	\begin{itemize}
		\item[$\diamond$] \emph{Incompleteness: }The algorithm is data-sensitive and cannot generalize to labelsets that do not appear into the training set
		\item[$\diamond$] \emph{Inefficiency: }Large $Y$ implies high training complexity and extremely few training examples for some newly mapped classes.
	\end{itemize}

	To overcome above issues while keeping LP's simplicity, Random k-Labelsets chooses to combine ensemble learning with LP. The latter is invoked only on random k-labelsets (each leading to a multi-class classifier $g_{y^k(l_r)}^+$) to guarantee computational efficiency and then ensemble a number of LP classifiers to achieve predictive completeness. For new instances $x$, two quantities are calculated: $\tau(\textbf{x},y_j)$, which counts the maximum number of votes that $y_j$ can receive from the ensemble and $\mu(\textbf{x},y_j)$, which counts the actual number of votes that $y_j$ receives from the ensemble. Therefore, the predicted labelset is calculated as follows: $Y = \{y_j|\mu(\textbf{x},y_j)/\tau(\textbf{x},y_j)>0.5,  1 \leq j \leq q\}$. This means that when the actual number of votes exceeds half of the maximum number of votes, $y_j$ is considered as a relevant label.For an ensemble created by n k-labelsets, the maximum number of votes on each label is $nk/q$ on average (usually: k=3 and n = 2q). Finally, another way to improve LP is to prune distinct label set in D appearing less than a pre-specified counting threshold.

	\subsection*{Algorithm Adaptation Methods}
	\addcontentsline{toc}{subsection}{Algorithm Adaptation Methods}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.9\textwidth]{aa.png}
		\caption{Algorithm Adaptation Methods}
		\centering
	\end{figure}

	\subsubsection*{Multi-Label k-Nearest Neighbor (ML-kNN)}
	\addcontentsline{toc}{subsubsection}{Multi-Label k-Nearest Neighbor (ML-kNN)}
	ML-kNN algorithm adapts k-nearest neighbor techniques utilizing maximum a posteriori (MAP) rule to make prediction by reasoning with the labeling information embodied in the neighbors. For new instances $x$, $N(x)$ represents the set of its k nearest neighbors identified in the dataset (similarity among instances is calculated by Euclidean distance). Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$. $C_j$ records the number of x’s neighbors with label $y_j$, while $H_j$ is the event that $\textbf{x}$ has the label $y_j$. Moreover, $P(H_j|C_j)$ is the posterior probability that $H_j$ can be applied in the condition that $\textbf{x}$ has exactly $C_j$ neighbors. Similarly, $P(\neg H_j|C_j)$ needs to be calculated in order to decide if to include $y_j$ in the prediction. This will be computed using the Bayes' theorem:

	\begin{center}
		$\frac{P(H_j|C_J)}{P(\neg H_j|C_j)} = \frac{P(H_j) \cdot P(C_j|H_j)}{P(\neg H_j) \cdot P(C_j| \neg H_j)}$
	\end{center}

	Prior probabilities ($P(H_j)$ and $P(\neg H_j)$) are computed via the frequency counting strategy, where a smoothing parameter $s$ is used to control the effect of uniform prior on the estimation (usually $s=1$). In addition, likelyhoods $P(C_j|H_j)$ and $P(C_j| \neg H_j)$ are computed using two frequency arrays:
	\begin{itemize}
		\item $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
		\item $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
	\end{itemize}

	This algorithm is a first-order approach using Bayesian reasoning. The decision boundary can be modified on-line when new instances appear. Moreover, Through prior probabilities calculation class-imbalance issue can be overcome. However, since label correlations are ignored, some extensions are proposed that take into account label associations.

	\subsubsection*{Multi-Label Decision Tree (ML-DT)}
	\addcontentsline{toc}{subsubsection}{Multi-Label Decision Tree (ML-DT)}
	ML-DT adapts decision tree techniques using multi-label entropy to build a decision tree recursively. Let $T = \{(x_i, Y_i) | 1 \leq i \leq n \}$ be the multi-label dataset with n examples. The algorithm splits the $x$ vector at the feature $l$ that maximizes the information gain criterion. Moreover, dataset $T$ is split on the $l$-th feature valued $\theta$ into branches ($T^-$ \& $T^+$), where $x_{il} \leq \theta, x_i \in T^-$ and $x_{il} > \theta, x_i \in T^+$. This process is invoked recursively by treating each time one of the two branches as the new root node and terminates until some stopping criterion $C$ is met (e.g. child size). Each subset is treated as a new class and single-label entropy is computed. Any new instances are assigned the label of the majority of members of the leaf that they arrive.

	In order to ensure low computational cost and high efficiency, the algorithm assumes independence among the labels (first-order approach). However, extended strategies are proposes, such as pruning and ensemble strategies, so as to exploit label correlations as well.

	\subsubsection*{Ranking Support Vector Machine (Rank-SVM)}
	\addcontentsline{toc}{subsubsection}{Ranking Support Vector Machine (Rank-SVM)}
	Rank-SVM adapts maximum margin strategy, where $q$ linear classifiers are optimized to minimize empirical ranking loss and enabled to handle nonlinear cases with kernel tricks. The learning system is composed by those classifiers $W = \{w_j,b_j | 1 \leq j \leq q\}$, where $w_j \in \mathbb{R}^d$ and $b_j \in \mathbb{R}$ are the weight vector and the bias
	for the j-th class label $y_j$ respectively. Rank-SVM defines the system’s margin on $(x_i,Y_i)$ by considering its ranking ability on the relevant and irrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$, which are separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$. When the learning system is capable of properly ranking every relevant-irrelevant label pair for each training example, the classifier will return positive margin. For each new instances $x$, the algorithms retrieves a ranked list of label pairs.

	Moreover, non-linear problems can be solved through feature mapping and kernel trick, while convex quadratic programming problems can be solved by any QP solver. This algorithm is a second-order approach using pairwise label associations. Improvements can be achieved by: replacing ranking with hamming loss which can be cast as a general form of	structured output classification, accomplishing thresholding strategy with techniques other than stacking-style procedure and avoiding the problem of kernel selection by employing multiple kernel learning techniques to learn from multi-label data.

	 \subsubsection*{Collective Multi-Label Classifier}
	 \addcontentsline{toc}{subsubsection}{Collective Multi-Label Classifier}
	 This algorithm adapts maximum entropy principle, where correlations among labels are encoded as binary random vectors into a joint probability distribution function(pdf) and label correlations are encoded into the joint pdf as constraints. This is a second-order approach, where all label pairs are considered and not just the relevant-irrelevant ones. Let $H_p(x, y)$ represent the information entropy of $(x,y)$ given their distribution $p(\cdot , \cdot)$. The principle of maximum entropy assumes that the distribution best modeling the current state of knowledge is the one maximizing $H_p(x, y)$ subject to a collection K of given facts: $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set. The fact is expressed as constraint on the expectation of  some  function  over. Along with the normalization constraint on $p(\cdot , \cdot)$ , the constrained optimization problem can be solved with standard Lagrange Multiplier techniques. Any unseen instance $x$ is labeled with $Y = \underset{y}{\text{argmax }} P(y | x)$. Exact inference with arg max is only tractable for small label space, otherwise pruning strategies should be applied.

@@

 	\section*{Related Learning Methods}
 	\addcontentsline{toc}{section}{Related Learning Methods}
 	Four learning methods are mentioned in this paper, which can be found below:
 	\begin{enumerate}
 		\item \textbf{Multi-instance learning: }This method studies the problem where each example is described by a bag of instances while associated with a single/binary label. Bag is assigned positive label in case of at least one positive member. Finally, it models complex semantics of $x_i$ in input space rather than its output.
 		\item \textbf{Ordinal classification: }This method assumes that labels are related through a natural ordering and instead of explicit class relevance, it assumes an ordering of relevant between labels via a membership vector. Finally, the multi-label problem is transformed into a set of ordinal set of problems.
 		\item \textbf{Multi-task learning: }This method studies the problem where multiple tasks are trained in parallel, sharing information, where knowledge from related tasks is used as an inductive bias to help improve the generalization performance of other tasks. The  tasks can be in the same feature space or different feature spaces, while in multi-label learning all the examples share the same feature space. Finally, in multi-task learning it is not reasonable to have a large number of tasks, while in multi-label learning it is usual to deal with large label space.
 		\item \textbf{Data streams classification: }This method studies the problem	where real-world objects are generated online and processed in a real-time manner. Key factor is to deal with the concept drift problem. Some existing strategies are: classifiers update significantly whenever a new batch of examples arrive, assumption that the influence of past data gradually declines as time evolves or change detector alerting whenever a concept drift is detected.
 	\end{enumerate}

	\section*{Conclusion}
	\addcontentsline{toc}{section}{Conclusion}
	Summarizing all the above, this paper defines the multi-label learning problem, presents 8 multi-label learning representative algorithms and mentiones some additional related learning methods. Some important future goals are the formal characterization on the underlying concept/mechanism on the appropriate usage of label correlations (especially on large output spaces) and also a thorough experimental comparative study to discover the advantages and disadvantages of different multi-label learning algorithms. Below, some online resources on multi-label learning are presented:

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\textwidth]{online.png}
		\caption{Online resources for Multi-Label Learning}
		\centering
	\end{figure}

	%-------------------------------------------------------------------------------
	% REFERENCES
	%-------------------------------------------------------------------------------
	\addcontentsline{toc}{section}{Related Work}
	\renewcommand\bibname{Related Work}
	\begin{thebibliography}{9}
		\bibitem{comp} 
		Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
		\bibitem{overview} Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
		\bibitem{correlations} Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
	\end{thebibliography}
\end{document}

>>>>

\documentclass[12pt]{report}
\usepackage[a4paper]{geometry}
\usepackage[myheadings]{fullpage}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx, wrapfig, subcaption, setspace, booktabs}
\usepackage[T1]{fontenc}
\usepackage[font=small, labelfont=bf]{caption}
\usepackage{fourier}
\usepackage[protrusion=true, expansion=true]{microtype}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{url, lipsum}
\usepackage{listings}
\usepackage{float}
\usepackage{todonotes}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{bm}
\graphicspath{{images/}}

@@

	\begin{itemize}
		\item \textbf{Example-based: }This kind of metrics evaluate multi-labeled performance on each example and then the result is spread to the whole dataset. The metrics are divided into two perspectives:
      \todo{Form them up into a table}
		\begin{itemize}
			\item Classification:
        \begin{table}
          \centering
          \begin{tabular}{cc} 
          \toprule
            one & two \\
          \midrule
            one & two \\
            one & two \\
          \bottomrule
          \end{tabular}
          \caption{Evaluation metrics for multi-label learning}
          \label{label:evaluation_metrics}
        \end{table}

@@

	\subsection*{Problem Transformation Methods}
  We move on to present the first category of methods, which transform the
  multi-label problem into a set of single label methods. See figure \ref{figure:ptm} for an overview of the approaches examined.

	\addcontentsline{toc}{subsection}{Problem Transformation Methods}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.9\textwidth]{pt.png}
		\caption{Problem Transformation Algorithms}
		\centering
    \label{figure:ptm}
	\end{figure}

@@

	\subsubsection*{Claibrated Label Ranking}
	\addcontentsline{toc}{subsubsection}{Claibrated Label Ranking}
	This algorithm transforms the learning problem into a label pairwise
  comparison ranking problem. For $q$ labels, $q(q-1)/2$ binary classifiers are
  constructed to discriminate between each label pair via a binary
  classification algorithm $h_{jk}(x)$. Firstly, respective pairwise training
  sets $D_{jk}$ are constructed, where $D_{jk}: \{x_i, Y_i | y_j \in Y_i \oplus
  y_k \in Y_i\}$, i.e. each $D_{jk}$ contains examples either in class $j$ or
  $k$. The learning system votes for each example and if $h_{jk}(x)>0$, then
  $x_i$ is associated with label $y_j$, otherwise $y_j$ is irrelevant and $x_i$
  is assigned to $y_k$. For unknown instances, all classifiers' votes are
  aggregated and ranked. In addition, a virtual label $y_v$ is used as an
  artificial splitting point between relevant and irrelevant labels, serving as
  a decision threshold for label relevance.

	This is a second-order approach algorithm using a one-vs-one scheme. The
  advantage of this method is that it smooths out the class-imbalance problem
  (where the number of a class positives is much less than the other's class
  positives) by operating on label pairs. The disadvantage is that the number of
  classifiers is quadratic to $|Y|$, compared to linear for Binary Relevance or
  Classifier Chains algorithms. However, the performance can be improved by
  using pruning methods to reduce the search space.

	\subsubsection*{Random k-Labelsets}
	\addcontentsline{toc}{subsubsection}{Random k-Labelsets}
	The random k-labelsets algorithm transforms the multi-label learning problem
  into an ensemble of multi-class classification problems. Each such partition
  targets a random subset of $\mathbb{P}(Y)$, limited to subsets present in the
  training dataset $X$, classifying it using Label Powerset (LP) techniques. In
  more detail, the multi-label dataset is transformed into single-label by
  treating each distinct labelset as a new class. Thus, each training example
  mapped to a new single class and classified through some single-label
  classification method. An instance $x_i$ is assigned to label $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible that this label can get. For unseen instances $x$, LP predicts its associated label set $Y$ by querying the prediction of multi-class classifier and then mapping it back to the power set of $Y$.

	This is a high-order approach algorithm since it utilizes a variety of label correlations. However, there are two limitations in terms of practical feasibility: 
	\begin{itemize}
		\item[$\diamond$] \emph{Incompleteness: }The algorithm is data-sensitive and cannot generalize to labelsets that do not appear into the training set.
		\item[$\diamond$] \emph{Inefficiency: }A large label set $Y$ implies high training complexity and extremely few training examples for some newly mapped classes.
	\end{itemize}

	A simple but powerful modification is the Random k-Labelsets variant, which
  runs an ensemble of executions, each with $k$-sized label sets. The ensemble
  scheme imporives on the predictive completeness of the system, while the
  limited labelset size guarantees computational efficiency. Additionally,
  pruning distinct labelsets which are less frequent than a lower threshold is
  another strategy to improve the method's performance.

	\subsection*{Algorithm Adaptation Methods}
  The next category refers to algorithm adaptation methods, i.e. strategies that
  directly address the multi-label nature of the problem. See figure
  \ref{figure:aam} for an overview of the approaches examined.

	\addcontentsline{toc}{subsection}{Algorithm Adaptation Methods}

	\begin{figure}[H]
		\centering
		\includegraphics[width=0.9\textwidth]{aa.png}
		\caption{Algorithm Adaptation Methods}
		\centering
    \label{figure:aam}
	\end{figure}

	\subsubsection*{Multi-Label k-Nearest Neighbor (ML-kNN)}
	\addcontentsline{toc}{subsubsection}{Multi-Label k-Nearest Neighbor (ML-kNN)}
	The ML-kNN algorithm adapts nearest neighbor techniques to the multi-label
  setting by utilizing the maximum a posteriori (MAP) rule, to make a prediction
  by reasoning with the labeling information embodied in the neighbors. For new
  instances $x$, $N(x)$ represents the set of its $k$ nearest neighbors
  identified in the dataset by a specified similarity or distance measure. Let
  $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in
  Y_k)]$, where $H_j$ is the event that $\textbf{x}$ has the label $y_j$ and
  $C_j$ records the number of x’s neighbors with label $y_j$. Moreover,
  $P(H_j|C_j)$ is the posterior probability that $H_j$ holds in the condition
  that $\textbf{x}$ has exactly $C_j$ neighbors. The posteriors $P(H_j|C_j)$ are
  calculated using Bayes' theorem with respect to the priors and the likelihoods.

	The prior probabilities ($P(H_j)$, $P(\neg H_j)$) are computed via a frequency counting strategy, where a smoothing parameter $s$ is used to control the effect of uniform prior on the estimation (usually $s=1$). In addition, likelihoods $P(C_j|H_j)$ and $P(C_j| \neg H_j)$ are computed using two frequency arrays:
	\begin{itemize}
		\item $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
		\item $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
	\end{itemize}

	This algorithm is a first-order approach that uses Bayesian reasoning. Being a
  nearest-neighbour method, the decision boundary can be modified on-line when
  new instances appear. Moreover, the use of prior probabilities can amend the
  class imbalance issue to a degree. A number of extensions have been proposed that take into account label associations.

	\subsubsection*{Multi-Label Decision Tree (ML-DT)}
	\addcontentsline{toc}{subsubsection}{Multi-Label Decision Tree (ML-DT)}
	This method adapts decision tree techniques for multi-label classification.
  Using the multi-label entropy measure, decision tree is built recursively by
  splitting features that yield the maximum information gain. Let $T = \{(x_i,
  Y_i) | 1 \leq i \leq n \}$ be the multi-label dataset with n examples. The
  algorithm splits the $x$ vector at the feature $l$ that maximizes the
  information gain criterion, where that value in $x$ is  $\theta$. This
  partitions the dataset $T$ into branches ($T^-$ \& $T^+$), where $x_{il} \leq
  \theta, x_i \in T^-$ and $x_{il} > \theta, x_i \in T^+$. This process is
  invoked recursively by treating each time one of the two branches as the new
  root node and terminates until some stopping criterion $C$ is met (e.g.
  subtree size). Each label subset is treated as a new class and single-label entropy is computed. Any new instances are assigned the label of the majority of members of the leaf that they arrive.

	In order to ensure low computational cost and high efficiency, the algorithm
  assumes independence among the labels; thus, it is a first-order approach.
  Extensions are proposed to reduce computational cost and exploit label interrelations, such as pruning and ensemble strategies.

	\subsubsection*{Ranking Support Vector Machine (Rank-SVM)}
	\addcontentsline{toc}{subsubsection}{Ranking Support Vector Machine (Rank-SVM)}
	Rank-SVM adapts the maximum margin strategy to the multi-label classification
  problem. $q$ linear classifiers are optimized to minimize the empirical
  ranking loss. The learning system is composed by classifiers that distinguish
  between relevant and irrelevant pairs. Each classifier is parameterized with $W = \{w_j,b_j | 1 \leq j \leq q\}$, where $w_j \in \mathbb{R}^d$ and $b_j \in \mathbb{R}$ are the weight vector and the bias
	for the j-th class label $y_j$ respectively. Rank-SVM defines the system’s
  margin on $(x_i,Y_i)$ by considering its ranking ability on the relevant and
  irrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$, which are
  separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i
  \right> + b_j - b_k=0$. The margin is defined as the minimum distance from all
  related-unrelated pairs and is minimized along with the training loss
  function. At consistent training, the classifier will return positive margin.
  For new test instances, the algorithms retrieves a ranked list of label pairs
  according to the signed distance to the decision hyperplane.

	Non-linear problems can be managed by exploiting kernel feature mapping via
  the kernel trick, which is popular in SVM methods. The optimization method is
  a convex quadratic programming problems and can thus be solved by any QP
  solver.
  This algorithm is a second-order approach using pairwise label associations.
  It is adaptable to a variety of tasks and data by using alternative loss
  functions and kernel feature mapping. Kernel selection can be accomplished by
  multiple kernel learning (MKL) techniques.

  \subsubsection*{Collective Multi-Label Classifier}
	 \addcontentsline{toc}{subsubsection}{Collective Multi-Label Classifier}
   The CML method is a multi-label variant of Conditional Random Field methods.

	 This algorithm involves the maximum entropy principle, where correlations
   among labels are encoded as binary random vectors into a joint probability
   distribution function and label correlations are encoded into the
   distribution as constraints.
   The conditional $p(\bm{y} | x)$ is computed via the maximum entropy
   criterion, where the information entropy measure $H_p(x,\bm{y})$ is maximized subject to each constraint.
   The latter are modeled as $ \mathbb{E} [ f_k(x,\bm{y}) ] = F_k  $, where $F_k$ is
 learned from the traininng data.
 The optimal solution is arrived at via Lagrange multipliers, assuming gaussian
 priors for the variables involved, and has the form of a Gibbs probability
 distribution.
 Test instances are labelled with respect to $\text{argmax}_y\text{ }p(\bm{y} | x)$.

   This is a second-order approach, where all label pairs are considered and not
   just the relevant-irrelevant ones which was the Rank-SVM approach. It is a
   convex constraint optimization problem, and is thus solvable by off the shelf
   CP solvers. The argmax operation during inference is expensive, which renders
   the method very computationally inefficient for large label spaces, if
   pruning is not applied. Varying the expression form of the constraints gives rise to difference
   version of the CML method.

@@

 	\section*{Related Learning Methods}
 	\addcontentsline{toc}{section}{Related Learning Methods}
 	Four related learning methods are mentioned in this paper, which can be found below:
 	\begin{enumerate}
 		\item \textbf{Multi-instance learning: }This method studies the problem
      where each example is described by a bag of instances while associated
      with a single binary label. The bag is assigned a positive label in the
      case of at least one positively labelled member. It models complex semantics of $x_i$ in input space rather than its output.
 		\item \textbf{Ordinal classification: } This scheme assumes label relevance
      to an instance is not binary but graded, producing a vector of ordinal graded
      membership of $x$ to a label. Multi-label classification is induced via a
      transformation of the original problem into a set of ordinal problems.
 		\item \textbf{Multi-task learning: }This method studies the problem where
      multiple tasks are trained in parallel. Tasks can share information, and
      knowledge from related tasks is used as an inductive bias to help improve
      the generalization performance of other tasks. The  tasks can share a
      common feature space or use different representations, as is common in
      multi-label learning. In this setting, it is reasonable to have small task
      workloads, since the execution is of a parallel nature. 
 		\item \textbf{Data streams classification: } Here, data is generated in real
      time, corresponding to the real-time nature of some task. Apart from the
      tight temporal constraints, the defining challenge here is the concept
      drift problem, where the concept classified can change over time. A common
      strategy to this effect is to gradually discount the significance of past
      data in favor of newly arrived batches.

 	\end{enumerate}

	\section*{Conclusion}
	\addcontentsline{toc}{section}{Conclusion}
	Summarizing, this paper defines the multi-label learning problem, presenting 8
  multi-label learning representative algorithms, mentions some additional
  related learning settings. Some important future goals are the formal
  characterization on the underlying concept and / or mechanism on the
  appropriate usage of label correlations (especially on large output spaces).
  In addition, thorough experimental comparative studies are essential to
  discover the advantages and disadvantages of different multi-label learning
  algorithms, so as to aid the conquest of the aforementioned theoretical goal.
  Some online resources on multi-label learning are presented on figure \ref{figure:resources}.

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\textwidth]{online.png}
		\caption{Online resources for Multi-Label Learning}
    \label{figure:resources}
	\end{figure}

	%-------------------------------------------------------------------------------
	% REFERENCES
	%-------------------------------------------------------------------------------
	\addcontentsline{toc}{section}{Related Work and Bibliography}
	\renewcommand\bibname{Related Work and Bibliography}
	\begin{thebibliography}{9}
		\bibitem{comp} 
		Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
		\bibitem{overview} Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
		\bibitem{correlations} Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010

\bibitem{trees} Vens, Celine, et al. "Decision trees for hierarchical multi-label classification." Machine Learning 73.2 (2008): 185-214.
\bibitem{rkl} Tsoumakas, Grigorios, and Ioannis Vlahavas. "Random k-labelsets: An ensemble method for multilabel classification." Machine learning: ECML 2007 (2007): 406-417.
\bibitem{mlknn} Zhang, Min-Ling, and Zhi-Hua Zhou. "ML-KNN: A lazy learning approach to multi-label learning." Pattern recognition 40.7 (2007): 2038-2048.
\bibitem{rksvm} Elisseeff, André, and Jason Weston. "A kernel method for multi-labelled classification." Advances in neural information processing systems. 2002.
\bibitem{cml}  Ghamrawi, Nadia, and Andrew McCallum. "Collective multi-label classification." Proceedings of the 14th ACM international conference on Information and knowledge management. ACM, 2005.
\bibitem{ordinals}  Cheng, Weiwei, Eyke Hüllermeier, and Krzysztof J. Dembczynski. "Graded multilabel classification: The ordinal case." Proceedings of the 27th international conference on machine learning (ICML-10). 2010.

	\end{thebibliography}
\end{document}
